---
title: "Enlightened London Telegram"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapsed: false
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs", output_file ="index.html") }) 
---

```{r, echo=FALSE}
htmltools::img(src = knitr::image_uri("telegram_logo.png"), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:20px;')
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lubridate)
library(mapview)
library(sp)
library(leaflet)
library(tidyverse)
library(kableExtra)
```

## Welcome {#welcome}
Welcome to the landing page for the London Enlightened Telegram community. Telegram is a chat app that many Enlightened agents around the world use to coordinate their activities, plan operations, meet for socials, and to swap cake recipes + cat memes. We presume you are here because you might be interested in things like that.

## Getting set-up on Telegram {#telegramsetup}
What to do now?  First, make sure you have [Telegram installed](https://telegram.org/) on your phone or mobile device. Then [set your Telegram username](https://telegram.org/blog/usernames-and-secret-chats-v2) to be your agent name (or something similar if it's already taken e.g. 'DrManBun-Enl').

Optionally, if you have an android phone, you might consider replacing the Telegram app with [Plus Messenger](https://play.google.com/store/apps/details?id=org.telegram.plus). It still *is* Telegram, but with a nicer interface and some additional options.

## For new players {#newplayers}
Have a look through the [new player chat rooms](#newplayerchatrooms) below, find your local region, and click on the link. This will add you to a chat room with a few local Enlightened agents who can talk you through any questions you have about the game, and in time give you permission to join the ['Verified'](#verifiedplayers) chat room for your area. By the way, as we are the green team, we're known as the frogs (and therefore as a new or unverified player, you're known as a tadpole!)


## New player chat rooms {#newplayerchatrooms}
|  Area              |  New players                                                           |
|:------------------:|:----------------------------------------------------------------------:|
| East London        | [East London Tadpoles](https://t.me/joinchat/CLM_hFKd6xNQcn8Oq8GycQ)   |
| West London        | [West London Tadpoles](https://t.me/joinchat/FbRZXVDEN2lND-zbwAzTSw)|
| North London       | [North London Tadpoles](https://t.me/joinchat/B_VxgUxXCJTux2zDf4YK2Q)  |
| South London       | [South London Tadpoles](https://t.me/joinchat/CLM_hEYFlIjFAbVwz3UtAQ)  |

```{r include = F}
x    <- seq(as.Date(Sys.Date()), as.Date(Sys.Date()) %m+% months(1), by="1 day")
date <- x[wday(x,label = TRUE) == "Fri" & day(x) <= 7]
```

## For verified players {#verifiedplayers}
The links below are for Enlightened agents who are already active members of their local community, and known to players of that area. To join these rooms you will need to be a member of the [London Enlightened Rocks community](https://enlightened.rocks/comm/edYMS1vp.com), and your Telegram account will need to be linked to your [Rocks profile](https://enlightened.rocks/me). If either of these things aren't correct, the links will not work for you. Think they should be working but aren't? Talk to a local agent for help.

## Verified player chat rooms {#verifiedplayerchatrooms}
```{r echo = F, warning=F}
east_london    <- 'https://t.me/joinchat/CLM_hFVUb8CPcIQqRAZ9Xw'
north_london   <- 'https://t.me/joinchat/B_VxgRXc-UjzSi7zLTz4XQ'
south_london   <- 'https://t.me/joinchat/CLM_hESoOFMBuCLORpF1fQ'
west_london    <- 'https://t.me/joinchat/FbRZXUypYXvHi2snHOx3ZQ'
general_london <- 'https://enl.rocks/-ROum'

tibble(Local_Chat_URL     = c(east_london, north_london, south_london, west_london),
       Local_Chat_Text    = c('East London', 'North London', 'South London', 'West London'),
       Regional_Chat_URL  = rep(general_london, 4),
       Regional_Chat_Text = rep('London', 4)) %>%
  mutate(Local           =  cell_spec(Local_Chat_Text, "html", link = Local_Chat_URL)) %>%
  mutate(Regional        = cell_spec(Regional_Chat_Text, "html", link = Regional_Chat_URL)) %>%
  select(Local, Regional) %>%
  kable("html", escape = FALSE, align="c") %>%
  collapse_rows(columns = 2, valign = "middle") %>%
  kable_styling(bootstrap_options = c("hover", "condensed"))

```
## Social events
The Enlightened in London are a pretty social bunch. We meet (at least) once per week in a bar or cafe for a chat/drink, and normally build some high level portals so that we can hack high level kit together. If you're a verified player, you can join our event announcement Telegram room by clicking this link (not-verified players will be automatically booted).

* [Enlightened London Events](https://t.me/joinchat/CLM_hE6KgWDEdBXCrsPHMQ)

If you've not been to one before, we'd love you to join us! Our next *public* event is on `r paste(day(date), months(date), year(date) )` at [LOCATION TBC](). People normally arrive from about 6:30pm onwards. If you're worried about finding us, don't. We are easy to spot. Please come over and introduce yourself. Failing that, ask in the [new players chat room](#newplayerchatrooms).


## Ingress Intel Total Conversion
If you haven't found it yet, there's an online Ingress map. You can browse areas of the world to see portals and links, and if you're inclined, use it to plan your fields (or which areas to destroy!). The standard version of this map can [be found here](https://ingress.com/intel), viewable through a web-browser. However some clever people have an overlay for it, called IITC. It's like the standard map, but in an app, and with more options. You can find [more details about it here](https://iitc.me/).

## Useful bots and channels
There are a number of news channels and bots in Telegram that you might want to look at. Here's a few of our favourites.

* [IngressMosaikBot](https://telegram.me/IngressMosaikBot) - A bot that will show you banner missions near the location you send it
* [Enlightened Today](https://telegram.me/IEToday) - Enlightened news, facts and fun from around the world
* [V Bot](https://telegram.me/vtgadminbot) - A bot for V related things
* [Rocks Bot](https://telegram.me/RocksBot) - A bot for Rocks related things
* [IUENG](https://t.me/IUENG) - Crossfaction Ingress Updates in English, particularly good for anomalies
* [EnlightenedUK](https://t.me/enlightenedUK) - Enlightened Ingress news - UK focused

## Community rules
Players in the London Enlightened adhere to the [Ingress community guidelines](https://support.ingress.com/hc/en-us/articles/206606858-Ingress-Community-Guidelines), in particular 'one accout one player', and no 'using tools or techniques to alter or falsify your location'. It ruins the game. Please don't do it. In addition, please remember this is a game. The Resistance players are our opposition and (in-game) enemy, but they're people just like you or I. Name-calling and/or posting specific details about people 'real lives' isn't cool.

## Other platforms
* [Ingress Enlightened UK on Facebook](https://www.facebook.com/EnlightenedUK/)
* [Enlightened UK Blog](https://enlighteneduk.blog/)
